Conflict-Free Vertex Coloring of Planar Graphs

### 2017-04-10 presentation/presentation.tex
Adding future work to presentation

>>>>

  \begin{frame}
    \frametitle{Future Work}

    \begin{itemize}
      \item Finding bounds and properties on specific graphs such as outerplanar graphs, interval graphs, hypergraphs, and more.
      \pause
      \vfill
      \begin{itemize}
        \item Allows for accurate estimates when applying conflict-free coloring to real-world problems.
      \end{itemize}
      \pause
      \vfill
      \item Variations of conflict-free coloring such as requiring \textbf{another} vertex to have a unique color within the neighborhood of a selected vertex.
      \pause
      \vfill
      \begin{itemize}
        \item Guiding a robot (unique color 1) to a destination (unique color 2).
      \end{itemize}
    \end{itemize}
